\documentclass[11pt]{article}
\usepackage{fontspec}
\usepackage[utf8]{inputenc}
\setmainfont{Bodoni 72 Book}
\usepackage[paperwidth=11in,paperheight=17in,margin=1in,headheight=0.0in,footskip=0.5in,includehead,includefoot,portrait]{geometry}
\usepackage[absolute]{textpos}
\TPGrid[0.5in, 0.25in]{23}{24}
\parindent=0pt
\parskip=12pt
\usepackage{nopageno}
\usepackage{graphicx}
%\usepackage{xcolor}
\usepackage[dvipsnames]{xcolor}
\graphicspath{ {./images/} }
\usepackage{amsmath}
\usepackage{tikz}
\newcommand*\circled[1]{\tikz[baseline=(char.base)]{
            \node[shape=circle,draw,inner sep=1pt] (char) {#1};}}

\begin{document}

\begingroup
\begin{center}
\huge \textbf{\textcolor{blue}{E S} \textcolor{olive}{C H} A T \textcolor{red}{O N}}
\end{center}
\endgroup

\begingroup
\begin{center}
\textcolor{magenta}{( or, \textit{ihr} \textit{| wir} )} \\ \textcolor{lightgray}{Hlynn}
\end{center}
\endgroup

\vspace*{2\baselineskip}

\begingroup
lied to. ( here, in a place as old as any other, saw a child in battle. their claw deep in a quarter of bread, barked at, bare toe nails scraping the jagged concrete like a knife testing crust. ) it happened. no reason to believe it didn't. trust. hunger. and if blame, then forgiven. gentleness insofar as the deserved pain is felt. the retributive anxiety. ( every word interrupted by a cough or wheeze of lungs damaged by small pieces of metal, carcinogen, and psychoactives. ) lied to. no reason to believe it didn't.
\endgroup

\begingroup
\begin{center}
\leftskip0.5in
\textcolor{lightgray}{Thread, she speaks. In knots.}
\rightskip\leftskip
\end{center}
\endgroup

\begingroup
\begin{center}
\textcolor{olive}{Das älteste Wort in der ältesten Sprache ist „Ama“. \\ Es ist Sumerisch und bedeutet „Mutter“. \\ Ich fand das immer herzzerreißend: \\ Solange es eine aufgezeichnete Sprache gibt,}
\end{center}
\endgroup

\begingroup
\begin{center}
\textit{\textcolor{blue}{It's been seventeen years. \\ Anything? \\ I'm to trace the very edge of the tip of my third finger \\ From the center of your forehead, just below the hairline, to the space between your eyebrows; \\ A becoming your profile of my finger; \\ As to maintain precise pressure from your hair to the underside of your chin, \\ Taking care after the brow, nose, the lips, \\ And then to grab one side of the jaw to each of my hands, \\ To torque my wrists towards me, \\ To see your eyes reflect the sky, and the sky your eyes, as the ocean to its superior? \\ And you would have me speak? \\ Sixteen years. } } \\ no reason to believe it didn't. 
\end{center}
\endgroup

\begingroup
\begin{center}
\textcolor{olive}{ist „Ama“. \\ Es ist Sumerisch und bedeutet „Mutter“.}
\end{center}
\endgroup

\begingroup
\begin{center}
\textcolor{red}{W H A T \hspace{10mm} D O \hspace{10mm} Y O U \hspace{10mm} R E M E M B E R} \\ \textcolor{magenta}{You. \\ And the leaves. }
\end{center}
\endgroup

\begingroup
lied. insofar as the deserved. was there a vision they had? ( yes, beneath the bridge, with a stranger. a needle in the arm, the \textcolor{olive}{Mutter} slashing with her voice through the forehead. ) you worried. you should be. trust. hunger. ( and there was blood on their mouth in the mirror, the pinks and purples and triteness of it all in a fog around her face, her voice. ) jesus, her voice, right at the front. they could feel it in their blood, like tar. maybe they lived. maybe they lived it. trust. you should be.
\endgroup

\begingroup
\begin{center}
\textcolor{magenta}{( It's you in the back, who raps on my shoulder and draws me through the doors; Who passes me through before I can catch up with you. You're in the rain, you're smiling. ) I've never seen someone . . . ( You raise your eyebrows and laugh, you gesture. I sit in the door. Light's drawn through the mist in colors over your head, beneath the canopy, and as they play around you, on you, with you - ) \\ I am too . . . \\ I was . . .}
\end{center}
\endgroup

\begingroup
\begin{center}
\leftskip0.5in
\textcolor{lightgray}{Thread, }
\rightskip\leftskip
\end{center}
\endgroup

\begingroup
\begin{center}
\textcolor{red}{A N D \hspace{10mm} W H E N  \hspace{10mm} Y O U  \hspace{10mm} C A N ' T  \hspace{10mm} R E M E M B E R  \hspace{10mm} M E} \\ \textcolor{magenta}{ I was . . . \\ And the leaves . . . } \\ \textcolor{red}{A N D \hspace{10mm} W H E N \hspace{10mm} Y O U \hspace{10mm} H E A R , \\ S P E A K ,  \\ N O \hspace{10mm} F O R M  } \\ \textcolor{magenta}{ I've never seen someone . . . } \\ \textcolor{red}{N O \hspace{10mm} F O R M \\} \textcolor{magenta}{I was . . .} \\ \textcolor{red}{A N D \hspace{10mm} W H E N \hspace{10mm} Y O U} \\ \textcolor{magenta}{I am too . . . } \\ \textcolor{red}{N O \hspace{10mm} F O R M}
\end{center}
\endgroup

\vspace*{1\baselineskip}

\begingroup
\begin{center}
\textcolor{olive}{Solange es eine aufgezeichnete Sprache gibt, \\ Solange es Sprache gibt, \\ Es gibt Familien, \\ Kinder. \\ Ich fand das immer herzzerreißend. \\ Die Kinder weinen, \\ sie weinen, weil etwas fehlt. \\ 
Sie rufen ,,Ama“, sie wissen nicht, was es bedeutet. \\ Immer herzzerreißend. \\ Für sie bedeutet es „Schmerz“. \\ Es bedeutet „hilf mir“. \\ ,,Etwas stimmt nicht“, \\ ,,Ama“, \\ ,,Etwas fehlt“, \\ ,,Ama“, ,,Ama“, \\ ,,hilf mir“, \\ ,,Ama“, \\ ,,Etwas fehlt“.}
\end{center}
\endgroup

\begingroup
you were told it looked like they had murdered someone. ( old bits of blood and wall all over the sheets, ) like tar. ( and there was blood on their mouth in the mirror. ) their teeth. ( naked and heaving with pieces of body and wall down the lips, the chin, ) the jaw to each of my hands. ( the claw, deep.  a child. ) ( a child. the \textcolor{olive}{Mutter.} )
\endgroup

\begingroup
\begin{center}
\textit{\textcolor{blue}{It's been sixteen years.}}
\end{center}
\endgroup

\begingroup
\begin{center}
\leftskip0.5in
\textcolor{lightgray}{she speaks.}
\rightskip\leftskip
\end{center}
\endgroup

\begingroup
( you, somewhere as old as any other, ) was there a vision? ( climbing out of the box, claw deep in a quarter of bread, locked eyes. he barked. ) \textcolor{olive}{,,Etwas fehlt“.} ( arms were buried in the shoulders, the axillae, and electromagnetic energy repelled. on the jagged concrete, hurt like hell, ) no reason to believe it didn't. \textcolor{olive}{,,Etwas stimmt nicht“.} ( then a palm became a forehead, fingers became the inferior incisors, )
\endgroup

\begingroup
\begin{center}
\textit{\textcolor{blue}{And you would have me speak? \\ As my palm learns the bone of your forehead, and my fingers the roots of your hair, \\ My left index exposing the red beneath your right eye, \\ My left fifth tracing the skyline of your inferior incisors, \\ Grazing the lips, thank god. \\ Finally. \\ It's been seventeen months. \\ You speak} \textcolor{lightgray}{in knots} \textcolor{blue}{through the fifth \\ As I'm to oscillate from between pressure of skin and pressure of bone. \\ You look up, \\ Waved her head, \\ Looking at each other like that } }
\end{center}
\endgroup

\begingroup
\begin{center}
\textcolor{red}{W H A T \hspace{10mm} D O \hspace{10mm} Y O U \hspace{10mm} R E M E M B E R} \\ \textcolor{lightgray}{Thread,} \\ \textcolor{magenta}{And the} \textcolor{olive}{Mutter.} \\ \textcolor{red}{N O \hspace{10mm} F O R M}
\end{center}
\endgroup

\begingroup
( the \textit{\textcolor{blue}{inferior incisors}} became the superior, with his cheek in the way. ) perhaps not. but the child wishes. the \textcolor{olive}{Kind} would have it go differently. \textcolor{olive}{,,Etwas fehlt“.} ( but neither the bread nor the old blood. these were there, right in front of them. ) no reason to believe. it didn't. \textit{\textcolor{blue}{And you would have me}} \textcolor{magenta}{. . .} \\ 
\begin{center}
\textit{\textcolor{blue}{fourteen years and seventeen months.}}
\end{center}
\endgroup

\begingroup
\begin{center}
\leftskip0.5in
\textcolor{lightgray}{she}
\rightskip\leftskip
\end{center}
\endgroup

\begingroup
\begin{center}
\textit{\textcolor{blue}{And you would have me}} \textcolor{lightgray}{speaks.}
\end{center}
\endgroup

\begingroup
\begin{center}
\textcolor{magenta}{. . .}
\end{center}
\endgroup

\begingroup
\begin{center}
\textcolor{magenta}{ I am too . . . } \\ ( climbing out of the ) \textcolor{magenta}{. . . \\  ( I am beneath the canopy with you, swinging. ) And one of us tells the other that we're stargazing, and that the white specks peeking through the green are the ones we're meant to see. ( If you tell me, it's sincere. If I tell you, I'm guessing what} \textit{\textcolor{blue}{you would have me}} \textcolor{magenta}{say. And the rocking is so gentle, ) perhaps you only notice by the movement of my shoulder against yours, ( reaching for a motion beyond our control. ) Your hair is red . . . \\ No . . . \\ Black . . . \\ No . . . \\ And I have read these rhythms to you before . . . \\ Maybe . . . \\ Your hair, it was . . . \\ I was too . . . }
\end{center}
\endgroup

\begingroup
\begin{center}
\textcolor{red}{Y OU \hspace{10mm} W E R E  \hspace{10mm} T O O \\ Y E S \\ A N D \hspace{10mm} T H E - } \\ \textcolor{magenta}{And the rainbow, it was still there. \\ The light that she . . . \\ When I . . . \\ In the rain . . . } \\\textcolor{red}{Y E S} \\ \textcolor{magenta}{ You're - She's smiling. I've never seen someone . . . } \\ \textcolor{red}{ A N D \hspace{10mm} W H E N \hspace{10mm} Y O U \hspace{10mm} C A N ' T , \\ E X P L A I N \hspace{10mm} I T \\ W I L L \hspace{10mm} Y O U ? \\ } \textcolor{magenta}{ I am too . . . } \\ \textcolor{red}{ W H I L E \hspace{10mm} Y O U \hspace{10mm} C A N ' T , \\ W I L L \hspace{10mm} Y O U ? \\ Y O U \hspace{10mm} A R E \hspace{10mm} T O O} \\ \textcolor{magenta}{We . . .}
\end{center}
\endgroup

\begingroup
\begin{center}
\leftskip0.5in
\textcolor{lightgray}{in}
\rightskip\leftskip
\end{center}
\endgroup

\begingroup
\begin{center}
\textcolor{olive}{,,Not“, die Kinder weinen, \\ ,,Ich habe Not“, \\ Aber das ist nicht das, was sie weinen. \\ Wie könnten sie, \\ Wenn ihr Bedürfnis zu dringend ist, um Zeit mit Sprache zu verschwenden? \\ Aber du zwingst sie. \\ Die Kinder werden zum Sprechen gezwungen. \\ Ohne Mitgefühl erzwingst du Sprache. \\ Du kannst ihr Weltbild nicht sehen, \\ Du weigerst dich. \\ Also rufen sie ,,Ama“. \\ Das ist alles, was sie tun können. }
\end{center}
\endgroup

\begingroup
\begin{center}
\textcolor{magenta}{I was . . . \\ We are . . .} 
\end{center}
\endgroup

\begingroup
\begin{center}
\textit{\textcolor{blue}{And you speak}} \textcolor{lightgray}{knots} \textit{\textcolor{blue}{to me, \\ As though you would have me untie.\\}} \textcolor{red}{W I L L \hspace{10mm} Y O U ?} \\ \textit{\textcolor{blue}{After eleven years? \\}} \textcolor{red}{W I L L \hspace{10mm} Y O U \hspace{10mm}} \textcolor{olive}{zwingen} \textit{\textcolor{blue}{me? \\}} \textcolor{olive}{Zwingen} \textit{\textcolor{blue}{my fifth beyond the incisors to the rear muscles of the tongue, \\ To find the}} \textcolor{lightgray}{knots,} \textit{\textcolor{blue}{\\ Assess them with my smallest digit}} \textcolor{magenta}{. . . \\} \textit{\textcolor{blue}{As though you would have}} \textcolor{magenta}{. . . \\} \textit{\textcolor{blue}{As though I could untie? \\ Would you? \\ After seventeen}} \textcolor{magenta}{. . . \\} \textit{\textcolor{blue}{No. \\ It cannot be done. \\ Whether you would have me or not, \\ It cannot be done. \\ And I will not do it. \\ Not with my hand on the back of your tongue. \\ Not with the heel pressing into the front lower teeth, \\ Not while they open, my elbows}} became \textit{\textcolor{blue}{your shoulders. \\ You}} \textcolor{magenta}{. . .} \textit{\textcolor{blue}{We}} would have it go differently. \\ \textit{\textcolor{blue}{It cannot be done. \\}} no reason. \\ it didn't. \\ no reason to believe. \\ \textit{\textcolor{blue}{After twenty - seven years, \\ my hand}} became \textit{\textcolor{blue}{your jaw, \\ In the second before you untie yourselves.}}
\end{center}
\endgroup

\begingroup
lied. ( the blood on the bread, the wall on the sheets. ) lied to. ( like they had murdered someone. ) this time they ran, ( no reason. ) the beard of their assailant brushed the back of their neck and their bare toe nails scraped the concrete, ( like a knife testing crust. ) their vision? lied to. ( the \textcolor{olive}{Mutter}'s voice slicing through the blood and the sheets. ) lied to. no reason. if anxiety, then retributive. ( the old bits of crumb and wall and blood on their chin, ) it was good. they don't want you to worry. it was all good. ( and they cleaned themself before they paid in cash. they told you that though they looked like a wild animal in the mirror, they could wash away the wall. it was all down the drain as easily as it fell onto the chin. they told you they ate together after, paid in cash. ) and it was all good. no reason. 
\endgroup

\begingroup
\begin{center}
\textcolor{olive}{Immer herzzerreißend.}
\end{center}
\endgroup

\begingroup
\begin{center}
\textit{\textcolor{blue}{And you speak,}}
\end{center}
\endgroup

\begingroup
\begin{center}
\textcolor{olive}{Ich fand das. }
\end{center}
\endgroup

\begingroup
\begin{center}
\textit{\textcolor{blue}{After five days.}}
\end{center}
\endgroup

\begingroup
\begin{center}
\textcolor{olive}{Die Mutter.}
\end{center}
\endgroup

\begingroup
\begin{center}
\textit{\textcolor{blue}{And you would have me speak. }}
\end{center}
\endgroup

\begingroup
\begin{center}
\textcolor{olive}{Ich fand das.}
\end{center}
\endgroup

\begingroup
\begin{center}
\textit{\textcolor{blue}{No.}}
\end{center}
\endgroup

\begingroup
\begin{center}
\textcolor{olive}{Die Kiefer flattern, die Lippen} \textcolor{magenta}{. . .}
\end{center}
\endgroup

\begingroup
\begin{center}
\textit{\textcolor{blue}{No. It cannot be done.}}
\end{center}
\endgroup

\begingroup
\begin{center}
\textcolor{olive}{Ich fand das.}
\end{center}
\endgroup

\begingroup
\begin{center}
\textcolor{red}{E X P L A I N \hspace{10mm} I T \\ W H I L E \hspace{10mm} Y O U \hspace{10mm}  C AN ' T \\} \textcolor{magenta}{I was . . . \\ } \textcolor{red}{W I L L \hspace{10mm} Y O U ? \\ } 
\end{center}
\endgroup

\begingroup
\begin{center}
\textit{\textcolor{blue}{No.}} \textcolor{magenta}{There was . . . \\ There is no rainbow through the green. Its time was beneath, a different one,} \textit{\textcolor{blue}{almost four years ago.}} \textcolor{magenta}{( There is only the light we are meant to see. ) So you say. ( So you say as you pull my lips onto the glass between us, ) you; somewhere above me. But I feel nothing. Not your lips. Not the glass. Nothing. Not your warmth. But you are right next to me? ( There, in the back. It's you. Smiling, in the rain. Smiling, beneath the green. Smiling, beneath only the stars we are meant to see. They're drawn in mist around you. ) You are so . . . Yes. You are so . . . Yes. You are so . . . \\ And I . . .} 
\end{center}
\endgroup

\begingroup
\begin{center}
\textcolor{red}{E X P L A I N \hspace{10mm} I T \\ N O \hspace{10mm}  F O R M \\ W H E N \hspace{10mm} Y O U \hspace{10mm} S P E A K \\} \textit{\textcolor{blue}{No.}} \textcolor{magenta}{Form.}
\end{center}
\endgroup

\begingroup
\begin{center}
\textcolor{magenta}{( Form in your lips on the glass between us. Form in these rhythms I have read to you before. Form in the stars we are meant to see. Form in the canopy, in the movement of my shoulder against yours.  Form in the light drawn through the mist in colors over your head. ) It was red . . .} 
\end{center}
\endgroup

\begingroup
\begin{center}
\textit{\textcolor{blue}{No.}}
\end{center}
\endgroup

\begingroup
\begin{center}
\textcolor{magenta}{Your hair, it was brown - Light brown.} 
\end{center}
\endgroup

\begingroup
\begin{center}
\textit{\textcolor{blue}{No.}}
\end{center}
\endgroup

\begingroup
\begin{center}
\textcolor{magenta}{Please, it was . . . \\ Black, it was . . .} 
\end{center}
\endgroup

\begingroup
\begin{center}
\textit{\textcolor{blue}{No.}}
\end{center}
\endgroup

\begingroup
\begin{center}
\textcolor{magenta}{All, it was all of them. It was all of them. It was all.} 
\end{center}
\endgroup

\begingroup
\begin{center}
\textit{\textcolor{blue}{No.}}
\end{center}
\endgroup

\begingroup
\begin{center}
\textcolor{red}{N O}
\end{center}
\endgroup

\begingroup
\begin{center}
\textcolor{magenta}{Who are you? \\ Tell me who you are. \\ All of you. \\ I don't know you. \\ My god, I don't know any of you . . .} 
\end{center}
\endgroup

\begingroup
\begin{center}
\textcolor{magenta}{. . .} 
\end{center}
\endgroup

\begingroup
\begin{center}
\textcolor{magenta}{. . .} 
\end{center}
\endgroup

\begingroup
\begin{center}
\textcolor{magenta}{. . .} 
\end{center}
\endgroup

\vspace*{2\baselineskip}

\begingroup
\begin{center}
{\setmainfont{Source Han Serif SC}\selectfont
\textcolor{OliveGreen}{( 我不会说话，\\ \vspace*{2\baselineskip} 也听不懂。\\ \vspace*{2\baselineskip} 但为了你, 我会努力的。)}
}
\end{center}
\endgroup

\end{document}